
\tab{ c | c c c c }{
\hline
& Factorization scale & Resummation scale & Renormalization scale & CKKW matching scale \\
\hline
\hline
     SR 2J  &  - & 7 & 7 & 9 \\
     SR 6J  &  9 & - & 23 & - \\
     SR Low-x  &  - & 11 & - & 6 \\
     SR High-x  &  19 & 7 & - & - \\
     SR 3B  &  36 & 15 & - & 19 \\
\hline
     VRa 2J  &  - & 8 & 12 & - \\
     VRa 6J  &  13 & 11 & - & - \\
     VRa Low-x  &  9 & - & 8 & 8 \\
     VRa High-x  &  - & 6 & - & 9 \\
     VRa 3B  &  20 & 16 & 7 & 6 \\
\hline
     VRb 2J  &  - & 4 & 3 & 7 \\
     VRb 6J  &  5 & - & 5 & 6 \\
     VRb Low-x  &  - & 5 & 6 & 5 \\
     VRb High-x  &  5 & - & - & 5 \\
     VRb 3B  &  - & 5 & 5 & 5 \\
\hline
}
{Theory systematics assigned for the post-fit yields for $\wjets$ [$\%$]. The numbers are shared by all the $\meffInc$-bins in the same SR/VR tower. Systematics contributing below 5$\%$ or 5 times less than that of the leading uncertainty in the region are ignored (labeled as "-"). }
{tab::Uncertainties::theoSys_Wjets}


\tab{ c | c c c }{
\hline
& Renormalization/factorization scale & tt+Wtb vs WWbb & Parton shower \\
\hline
\hline
     SR 2J  &  22 & 17 & 8 \\
     SR 6J  &  21 & 24 & 25 \\
     SR Low-x  &  15 & 13 & 10 \\
     SR High-x  &  15 & 17 & 28 \\
     SR 3B  &  27 & 25 & 13 \\
\hline
     VRa 2J  &  12 & 5 & 10 \\
     VRa 6J  &  15 & 7 & 9 \\
     VRa Low-x  &  10 & 12 & 6 \\
     VRa High-x  &  17 & 10 & - \\
     VRa 3B  &  13 & 26 & 8 \\
\hline
     VRb 2J  &  - & 21 & 10 \\
     VRb 6J  &  - & 19 & 5 \\
     VRb Low-x  &  - & 18 & 5 \\
     VRb High-x  &  - & 23 & 8 \\
     VRb 3B  &  - & 25 & 7 \\
\hline
}
{Theory systematics assigned for the post-fit yields for $\ttbar+Wt$ [$\%$]. The numbers are shared by all the $\meffInc$-bins in the same SR/VR tower. Systematics contributing below 5$\%$ or 5 times less than that of the leading uncertainty in the region are ignored (labeled as "-"). }
{tab::Uncertainties::theoSys_ttbar}


\tab{ c c c c c }{
\hline
\hline
& Factorization scale & Resummation scale & Renormalization scale & CKKW matching scale \\
\hline
     2J $\meffIncFirst$  &  - & - & 23 & 7 \\
     2J $\meffIncSecond$  &  - & - & 25 & - \\
     2J $\meffIncThird$  &  - & - & 25 & - \\
     6J $\meffIncFirst$  &  - & - & 35 & - \\
     6J $\meffIncSecond$  &  10 & - & 35 & - \\
     6J $\meffIncThird$  &  - & - & 39 & 15 \\
     Low-x  &  - & - & 33 & 10 \\
     High-x  &  - & - & 32 & - \\
     3B $\meffIncFirst$  &  \\
     3B $\meffIncSecond$  &  \\
\hline
}
{Theory systematics assigned for the yields of $\zjets$ [$\%$]. The uncertainty is shared by SRs and corresponding VRs. Systematics contributing below 5$\%$ or 5 times less than that of the leading uncertainty in the region are ignored (labeled as "-"). }
{tab::Uncertainties::theoSys_Zjets}


\tab{ c c c c }{
\hline
\hline
& Factorization scale & Resummation scale & Renormalization scale \\
\hline
     2J $\meffIncFirst$  &  25 & 10 & 16 \\
     2J $\meffIncSecond$  &  21 & 12 & 21 \\
     2J $\meffIncThird$  &  15 & 13 & 23 \\
     6J $\meffIncFirst$  &  8 & 9 & 19 \\
     6J $\meffIncSecond$  &  8 & 7 & 26 \\
     6J $\meffIncThird$  &  9 & 11 & 37 \\
     Low-x  &  13 & - & 22 \\
     High-x  &  - & 12 & 34 \\
     3B $\meffIncFirst$  &  15 & 7 & 29 \\
     3B $\meffIncSecond$  &  13 & 10 & 35 \\
\hline
}
{Theory systematics assigned for the yields of Di-boson [$\%$]. The uncertainty is shared by SRs and corresponding VRs. Systematics contributing below 5$\%$ or 5 times less than that of the leading uncertainty in the region are ignored (labeled as "-"). }
{tab::Uncertainties::theoSys_VV}


\tab{ c c c }{
\hline
\hline
& Renormalization/factorization scale & Hard processes \\
\hline
     2J $\meffIncFirst$  &  - & 9 \\
     2J $\meffIncSecond$  &  5 & 10 \\
     2J $\meffIncThird$  &  - & 16 \\
     6J $\meffIncFirst$  &  - & 8 \\
     6J $\meffIncSecond$  &  - & 17 \\
     6J $\meffIncThird$  &  - & 22 \\
     Low-x  &  - & 16 \\
     High-x  &  - & 33 \\
     3B $\meffIncFirst$  &  5 & 5 \\
     3B $\meffIncSecond$  &  - & 13 \\
\hline
}
{Theory systematics assigned for the yields of $\ttbar+V$ [$\%$]. The uncertainty is shared by SRs and corresponding VRs. Systematics contributing below 5$\%$ or 5 times less than that of the leading uncertainty in the region are ignored (labeled as "-"). }
{tab::Uncertainties::theoSys_ttV}

